%-------------------------
% Resume in Latex
% Author : Aniketh Tarikonda
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {#3} & {#4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Aniketh Tarikonda} \\ \vspace{2pt}
    \href{mailto:aniketh8@illinois.edu}{aniketh8@illinois.edu} $|$ 
    \href{https://anikethta.com}{anikethta.com} $|$
    \href{https://github.com/anikethta}{github.com/anikethta}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Illinois, Urbana-Champaign}{Champaign, IL}
      {Bachelor of Science in Computer Engineering, Minor in Physics}{Expected Dec. 2027}
    \resumeItemListStart
        \resumeItem{Honors: James Scholar, Dean's List (Fall 2024–Present), Member of IEEE-HKN Alpha Chapter}
        \resumeItem{Cumulative GPA: 3.97 / 4.00}
        \resumeItem{Relevant Coursework: Applied Parallel Programming (GPUs \& CUDA), Digital Systems Laboratory (FPGAs), Digital Signal Processing, Analog Signal Processing, Data Structures}
        \resumeItem{Planned Coursework: Computer Organization and Design, Intro to VLSI System Design}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
  {Eco Illini Supermileage}{Champaign, IL}
  {Electrical/Firmware Lead}{Aug. 2024 -- Present}
  \resumeItemListStart
    \resumeItem{Leading an interdisciplinary team of 20+ engineers to design, verify, and integrate electrical systems for new generations of electric vehicles.}
    \resumeItem{Designed schematics and PCBs for 3+ custom boards, including a power distribution unit and battery management system, following automotive standards (e.g., SAE J1939).}
    \resumeItem{Programmed custom STM32 microcontroller-based boards with firmware supporting SPI, UART, and CAN communication protocols.}
    \resumeItem{Validated hardware on 2+ boards, achieving reliable data transmission rates exceeding 99\%.}
    \resumeItem{Mentoring new members in automotive systems, embedded systems, and concepts in electrical engineering.}
    \resumeItemListEnd

    \resumeSubheading
      {ResearchBase Inc.}{Pleasanton, CA}
      {Software Engineering Intern}{July 2025 -- Aug. 2025}
      \resumeItemListStart
        \resumeItem{Built a ResearchCopilot prototype with a real-time conversational pipeline integrating automatic speech recognition (ASR) and analytics to surface insights dynamically.}
        \resumeItem{Improved document parsing accuracy by integrating LandingAI Agentic Document Extraction (ADE) APIs for structured data extraction.}
        \resumeItem{Developed a text-to-image generation feature using ChatGPT image APIs, converting natural language prompts into visuals.}
      \resumeItemListEnd

    \resumeSubheading
      {Alameda County IT Department}{Oakland, CA}
      {IT Intern}{June 2022 -- Aug. 2022}
      \resumeItemListStart
        \resumeItem{Migrated 2000+ current and archived requests between Axosoft and Atlassian Jira through the use of RESTful APIs.}
        \resumeItem{Coordinated with various subteams throughout the department in order to ensure all previously-used features would be preserved.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {GPT-2 Transformer Model Implementation}{}
          \resumeItemListStart
            \resumeItem{Implementing core components of the GPT-2 transformer model in CUDA, including encoder layers, GELU activation, and layer normalization, optimized for GPU parallelism.}
            \resumeItem{Deploying a custom GPT-2 inference pipeline on NCSA’s Delta HPC cluster, leveraging high-throughput compute nodes for performance evaluation.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} SystemVerilog, Verilog, C/C++, Python, Java, CUDA, JavaScript, bash \\
     \textbf{Tools:} Vivado, Vitis, Verilator, STM32CubeIDE, Postman, Linux, Altium Designer, KiCAD, Jira, oscilloscopes, function generators, gdb, git \\
     \textbf{Libraries/Frameworks:} NumPy, Node.js, React, Spring, PostgreSQL
     }}
 \end{itemize}

%-------------------------------------------
\end{document}